---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/news-r/ft.svg?branch=master)](https://travis-ci.org/news-r/ft)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/news-r/ft?branch=master&svg=true)](https://ci.appveyor.com/project/news-r/ft)
<!-- badges: end -->

# ft

Brings the [FT](https://www.ft.com/) Search API to R.

## Installation

You can install the package from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("news-r/ft")
```


## Setup

Create a free account at [developer.ft.com](https://developer.ft.com) to create an API key.

```r
ft_key("xxXXxxXx")
```

Note that you can specify the `FT_API_KEY` key as an environment variable in your `.Renviron` for convenience.


## Example

```{r}
library(ft)

# search 2 pages of articles "banks"
banks <- ft_search("banks", pages = 2)

# search titles of articles on "debates" and not Trump
debates <- ft_search("debates -Trump", curations = "ARTICLES", aspects = "title")
head(debates)
```

You can learn more about the possible `curations`, `aspects`, `facets`, `searchable`, and `sortable` with `?discover` which describes functions that return vectors of valid filters.

```{r}
ft_list_curations()
```